---
output:
  pdf_document: default
  html_document: default
---
# import lilbrary
```{r}
library(corrplot)
library(car)
library(leaps)
library(moments)
library(dplyr)
library(MASS)
library(psych)
library(GPArotation)
library(gvlma)
library(factoextra)
library(glmnet)
library(Matrix)
library(data.table)
library(lmtest)
library(ggplot2)
library(ggthemes)
```

# read the data
```{r}
Data <- read.csv("USBES_V2.csv")
head(Data)
```

# standardization
```{r}
Data_new<- Data_train[ , !colnames(Data_train) %in% c('credit.policy','purpose')]
Data_box<-scale(Data_new[1:7],center=FALSE)
Data_new <- cbind(Data_train[2],scale(Data_new[1:7],center=FALSE),Data_new[8:12])
head(Data_new)
```
```{r}
na.omit(Data)
full_model <- lm(FCH4_mean ~ ., data = Data)
anova(full_model)
summary(full_model)
```
```{r}
stepwise<-step(full_model)
summary(stepwise)
```

#Delete unrelated variables
```{r}
subData <- Data[ , colnames(Data) %in% c('FCH4_mean',"Year" , "DOY" , "TIMESTAMP_END,NEE" , "H" , "LE" , "FCH4_median" ,
    "USTAR" , "SW_IN", "NETRAD" , "PPFD_OUT", "VPD" , "RH" , "PA","TA" , 
    "TS_1" ,"TS_3", "G_1", "SWC_1" , "SWC_2", "GPP_DT" , "RECO_DT" , "H_F" , 
    "LE_F" , "FCH4_F" , "SW_IN_F", "LW_IN_F" , "NETRAD_F" , "PPFD_IN_F", 
    "PPFD_OUT_F" ,"VPD_F" ,"RH_F", "PA_F" , "WS_F" , "LE_F_ANN" , "FCH4_F_ANN_median" , 
    "FCH4_F_ANN_mean" ,"FCH4_uncertainty" , "WD_vec_avg" , "WS_vec_avg" , 
    "FCH4_daily_percent_NaN")]
submodel <- lm(FCH4_mean ~ ., data = subData)
summary(submodel)
# anova(submodel)
```
#stepwise regression
```{r}
stepwise_model<-step(submodel,direction="both")
summary(stepwise_model)
anova(stepwise_model)
```
#full subset regression
```{r}
regsub <- regsubsets(FCH4_mean ~ ., data = subData,method="seqrep", nbest = 4)
plot(regsub, scale = "adjr2",margin = 0.1);
plot(regsub, scale = "Cp",rsize=0.5,margin = 0.2)
```
#Determine influence points
```{r}
influencePlot(submodel)
```
#Determine outlier points
```{r}
outlierTest(submodel)
```

# Detect outlier and high leveage points
```{r}
Data_new <- subData[-c(902,514,590,901,877,349,910,624,338,210,913),]
```

#multicollinearity test
```{r}
vif(submodel)
```

#confidence interval
```{r}
confint(submodel)
```
# Show the importance of each factor
```{r}
relweights <- function(fit, ...) {
R <- cor(fit$model)
nvar <- ncol(R)
rxx <- R[2:nvar, 2:nvar]
rxy <- R[2:nvar, 1]
svd <- eigen(rxx)
evec <- svd$vectors
ev <- svd$values
delta <- diag(sqrt(ev))
# correlations between original predictors and new orthogonal variables
lambda <- evec %*% delta %*% t(evec)
lambdasq <- lambda^2
# regression coefficients of Y on orthogonal variables
beta <- solve(lambda) %*% rxy
rsquare <- colSums(beta^2)
rawwgt <- lambdasq %*% beta^2
import <- (rawwgt/rsquare) * 100
lbls <- names(fit$model[2:nvar])
rownames(import) <- lbls
colnames(import) <- "Weights"
# plot results
barplot(t(import), names.arg = lbls, ylab = "% of R-Square",
xlab = "Predictor Variables", main = "Relative Importance of Predictor Variables",
sub = paste("R-Square = ", round(rsquare, digits = 3)),
...)
return(import)
}
```

```{r}
model <- lm(FCH4_mean~. , data = Data_new)
dt<-relweights(model, col = "lightgrey")
```
# The importance scores
```{r}
dt
```

```{r}
hist(submodel$residuals)
skewness(submodel$residuals)
```
```{r}
plot(density(submodel$residuals),main = "Density of model residuals",lwd=2)
```
# Plot Q-Q graph
```{r}
par(mfrow=c(2,2)) 
plot(submodel)
```
# Cooke distance diagram
```{r}
plot(submodel, 4)
```

# Residuals and lever diagrams
```{r}
plot(submodel, 1)
```
# One of the Heteroscedasticity Test 
```{r}
gvmodel <- gvlma(submodel)
summary(gvmodel)
```

#Homovariance test: if p value is greater than 0.05, it can be considered to meet the assumption of the same variance 
```{r}
ncvTest(submodel)
```
#Independence test: when p value is greater than 0.05, errors can be considered to be independent of each other
```{r}
durbinWatsonTest(submodel)
```
```{r}
dwtest(submodel)
```
```{r}
spreadLevelPlot(submodel, lwd = 0.5, main = "Spread-Level plot for our finalmodel")
```








